---
title: "PM566 Hw2"
author: "Changqing Su"
date: "2020/9/23"
output: html_document
---

```{r,message=FALSE, echo=FALSE}
library(data.table)
library(leaflet)
library(tidyverse)
```



## Data Wrangling  

#### 1 

```{r}
indi <- data.table::fread("chs_individual.csv")
regi <- data.table::fread("chs_regional.csv")

chs1= merge(indi,regi, by= "townname")

nrow(chs1)
length(unique(chs1$sid))
```
There seems no duplicated rows after merging the data.


#### 2 

```{r}
chs1$obesity_level = ifelse(chs1$bmi<14,"underweight", 
                            ifelse(chs1$bmi>=14 & chs1$bmi<22, "normal",
                                   ifelse(chs1$bmi>=22 & chs1$bmi<24,"Overweight", 
                                          ifelse(chs1$bmi>=24,"obese",NA))
                                   )
                            )
a1=table(chs1$obesity_level)
a2=tapply(chs1$bmi, chs1$obesity_level, min)
a3=tapply(chs1$bmi, chs1$obesity_level, max)
a4=rbind(a1,a2,a3)
row.names(a4)=c("observation","bmi_min","bmi_max")
a4
```

#### 3

```{r}
chs1$smoke_gas_exposure=ifelse(chs1$smoke  == 1 & chs1$gasstove == 0, "secondhand_only",
                               ifelse(chs1$smoke ==0 & chs1$gasstove ==1, "gasstove_only",
                                      ifelse(chs1$smoke ==0 & chs1$gasstove ==0, "no_secondhand_or_gasstove", 
                                             ifelse(chs1$smoke ==1 & chs1$gasstove ==1,"both_secondhand_and_gasstove",NA)
                                             )
                               )
)
table(chs1$smoke_gas_exposure)                                          
```

#### 4

```{r}
#replace the NA values with mean for fev

for (i in 1:nrow(chs1))
  {
  if (is.na(chs1$fev[i])==T)
    {
    a=chs1$male[i]
    b=chs1$hispanic[i]
    chs1$fev[i]=mean(chs1$fev[which(chs1$male==a & chs1$hispanic==b)],na.rm = T)
  }
  

#check if it works
chs1$fev[which(is.na(chs1$fev)==T)]

#replace the NA values with mean for asthma
}
for (i in 1:nrow(chs1))
  {
  if (is.na(chs1$asthma[i])==T)
    {
    a=chs1$male[i]
    b=chs1$hispanic[i]
    chs1$asthma[i]=mean(chs1$asthma[which(chs1$male==a & chs1$hispanic==b)],na.rm = T)
  }
  

}

#check if it works
chs1$asthma[which(is.na(chs1$asthma)==T)]


#construct table for townname

t1=rbind(tapply(chs1$fev, chs1$townname,mean),
      tapply(chs1$fev, chs1$townname,sd),
      tapply(chs1$asthma, chs1$townname,mean),
      tapply(chs1$asthma, chs1$townname,sd)
)
row.names(t1)= c("fev mean","fev sd","asthma mean", "asthma sd")
t1

#construct table for sex

t2=rbind(tapply(chs1$fev, chs1$male,mean),
      tapply(chs1$fev, chs1$male,sd),
      tapply(chs1$asthma, chs1$male,mean),
      tapply(chs1$asthma, chs1$male,sd)
)
row.names(t2)= c("fev mean","fev sd","asthma mean", "asthma sd")
colnames(t2)=c("female","male")
t2

#construct table for obesity_level

t3=rbind(tapply(chs1$fev, chs1$obesity_level,mean),
      tapply(chs1$fev, chs1$obesity_level,sd),
      tapply(chs1$asthma, chs1$obesity_level,mean),
      tapply(chs1$asthma, chs1$obesity_level,sd)
)
row.names(t3)= c("fev mean","fev sd","asthma mean", "asthma sd")
t3

#construct table for smoke_gas_exposure

t4=rbind(tapply(chs1$fev, chs1$smoke_gas_exposure,mean),
      tapply(chs1$fev, chs1$smoke_gas_exposure,sd),
      tapply(chs1$asthma, chs1$smoke_gas_exposure,mean),
      tapply(chs1$asthma, chs1$smoke_gas_exposure,sd)
)
row.names(t4)= c("fev mean","fev sd","asthma mean", "asthma sd")
t4


```






## Looking at the Data (EDA)   


#### 1

```{r}

chs1 %>%
  filter(!(bmi %in% NA))  %>%
  ggplot(mapping = aes(x=bmi,y=fev,color=townname))+
  geom_point()+
  stat_smooth(method=lm)


```

The plot shows that there may exist positive relationship between bmi and fev.

#### 2

```{r}
chs1 %>%
  filter(!(obesity_level %in% NA))  %>%
  ggplot()+
  geom_histogram(mapping = aes(x=fev,fill=obesity_level))+
  scale_fill_brewer(palette = 'PuOr')



chs1 %>%
  filter(!(smoke_gas_exposure %in% NA))  %>%
  ggplot()+
  geom_histogram(mapping = aes(x=fev,fill=smoke_gas_exposure))+
  scale_fill_brewer(palette = 'PuOr')

```

The plot shows that the fev is normally distributed. Smoke/gas exposure are not associated with fev.

#### 3

```{r}


chs1 %>%
  filter(!(smoke_gas_exposure %in% NA))  %>%
  ggplot()+
  geom_bar(mapping = aes(x=obesity_level,fill=smoke_gas_exposure))+
  scale_fill_brewer(palette = 'PuOr')+
  labs(tilte='Barchart of BMI by smoke/gas exposure')+
  theme_bw()
```

Here, most people  have gas stove in their residences only.

#### 4 

```{r}

chs1 %>%
  filter(!(obesity_level %in% NA))  %>%
  ggplot(mapping = aes(x=obesity_level,y=fev))+
  stat_summary(fun.data = 'mean_sdl')



chs1 %>%
  filter(!(smoke_gas_exposure %in% NA))  %>%
  ggplot(mapping = aes(x=smoke_gas_exposure,y=fev))+
  stat_summary(fun.data = 'mean_sdl')
```

Here, we can see that people with higher bmi level may have higher fev value.  
But smoke/gas exposure seems to have no significant association with fev.
#### 5

```{r}

  comm_cat=colorNumeric(c('green','yellow','red'),domain = chs1$pm25_mass)

  chs1 %>%
  filter(!(pm25_mass %in% NA))  %>%
  leaflet()  %>%
  addProviderTiles('OpenStreetMap') %>%
  addCircles(lat=~lat,lng = ~lon, color = ~comm_cat(pm25_mass), opacity = 1, fillOpacity = 1, radius =100) %>%
  addLegend('bottomleft', pal=comm_cat, values = chs1$pm25_mass, title ='PM2.5 Mass', opacity= 1)
```

Here, we can see that Riverside community has the greatest PM2.5 Mass.


#### 6


```{r}
chs1 %>%
  filter(!(fev %in% NA))  %>%
  ggplot(mapping = aes(x=pm25_mass,y=fev))+
  stat_summary(fun.data = 'mean_sdl')

```

Here, the statistical summary plot shows that PM2.5 mass has no significant association with FEV.